---
title: "R Notebook"
output: html_notebook
---

Install the package `fBasics` first

```{r}
install.packages("fBasics")
```

Print working directory

```{r}
getwd()
```

Change working directory

```{r}
setwd('financial-time-series/chapter1')
```

Make sure the working directory is correct

```{r}
getwd()
```

Load the package `fBasics`

```{r}
library(fBasics) # load the package fBasics
da = read.table("../data/d-ibm3dx7008.txt", header = T) # load the data
# header=T means 1st row of the data file contains
# variable names. The default is header=F, i.e. no names
dim(da) # show the size of the data: rows columns
```
```{r}
da[1,] # print the first row of the data
```
```{r}
ibm = da[,2] # obtain IBM simple returns
sibm = ibm*100 # percentage simple returns
basicStats(sibm) # compute the summary statistics
```

nobs (sample size)
NAs	(# of missing values)
1. Quartile	(25th percentile)		
3. Quartile	(75th percentile)
Mean	(sample mean)
Median	(sample median)		
Sum	(sum of the percentage simple returns)
SE Mean	(standard error of the sample mean)
LCL Mean (lower bound of 95% conf. interval for mean)
UCL Mean (upper bound of 95% conf. interval for mean)
Variance (sample variance)
Stdev (sample standard error)
Skewness (sample skewness)
Kurtosis (sample excess kurtosis)

Alternatively, one can run individual commands
```{r}
mean(sibm)
```
```{r}
var(sibm)
```
```{r}
sqrt(var(sibm))
```
```{r}
skewness(sibm)
```
```{r}
kurtosis(sibm)
```
Simple tests
```{r}
n = length(sibm)
s1 = skewness(sibm)
t1 = s1/sqrt(6/n) # compute test statistic
t1
```

```{r}
pv = 2*(1-pnorm(t1)) # compute p-value
pv
```
Turn to log returns in percentages
```{r}
libm = 100*log(ibm + 1)
t.test(libm) # test mean being zero
```
The result shoes that the hypothesis of zero expected return cannot be rejected at the 5% or 10% level.
```{r}
normalTest(libm, method='jb') # normality test
```
The result shows the normality for log return is rejected. For more information about Jarque-Bera normality test see the paper "A Test for Normality of Observations and Regression Residuals"









